PAMELA: an annotation-based Java Modeling Framework

### 2022-03-10 experimentations.tex
tex names standardization

The full Openflexo infrastructure is composed of about 50 components. In most components, the PAMELA framework is extensively used. As an example the \texttt{diana} component\footnote{\url{https://diana.openflexo.org}} (a component providing diagraming features) is composed of 998 classes. 159 of those classes (mostly the diagraming model) are defined as Pamela \texttt{ModelEntity}.

@@

The PAMELA implementation is now really stable and mature. According to Openflexo infrastructure developers, maintenance of code base (about 10 years of development) raises no PAMELA-specific issue, while co-evolution of models and code is greatly improved compared to a "code generation"-based solution.

>>>>

The full Openflexo infrastructure is composed of about 50 components. In most components, the PAMELA framework is largely used. As an example the \texttt{diana} component\footnote{\url{https://diana.openflexo.org}} (a component providing diagraming features) is composed of 998 classes. 159 of those classes (mostly the diagraming model) are defined as Pamela \texttt{ModelEntity}.

@@

The PAMELA implementation is now really stable and mature. According to Openflexo infrastructure developers, maintenance of code base (about 10 years of development) raises no PAMELA-specific issue, while co-evolution of models and code is greatly improved compared to a 'code generation'-based solution.
